### 2020-02-08 results/sec_1-test_plan.tex
Update Obs Full test 24 and 48 request size

Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 5min intervals and create metadata of the timeseries
    \item Import Timeseries
    \begin{itemize}
        \item Plan for test run of 30 minutes. In each test run change the request size from 1hr, 30min and 5min. (total 1.5 hours)
        \item Have mixture of data: Scalar - 70\%(max 210 requests), Vector (Multi-Scalar) - 20\% (max 60 requests), Grid - 10\% (max 30 requests)
    \end{itemize}
    \item Extensions
    \begin{itemize}
        \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
        \item 30min of test run. Just for 5min data. (total 0.5 hours)
        \item Do with Import Timeseries with error data which will go through extensions.
    \end{itemize}
    \item Export Timeseries
    \begin{itemize}
        \item 30min test run. Change request size from 1hr, 30min and 5min. (total 1.5 hours)
        \item Have mixture of data: Scalar - 70\%, Vector (Multi-Scalar) - 20\%, Grid - 10\% (Use the Imported - Data before and verify against Extensions)
    \end{itemize}
    \item Import + Extension + Export + Timeseries Queries (All)
    \begin{itemize}
        \item 30min test run. Change with request size from 1hr, 30min and 5min. (total 1.5 hours)
    \end{itemize}
\end{enumerate}

While performance analysis following metrics are use to measure the performance of the system.
\begin{itemize}
    \item Throughput
    \item Latency
    \item Resource Utilization
    \item Auto Scaling
\end{itemize}

>>>>

\subsection{Test Plan Flow}
\label{subse:test_plan_flow}
Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals and create metadata of the timeseries
    \item Import Timeseries
    \begin{itemize}
        \item Plan for test run of 15 minutes with the request size of 15min data.(total 0.25 hours)
        \item Have mixture of data: Scalar - 70\%(max 210 requests per second), Vector (Multi-Scalar) - 20\% (max 60 requests per second), Grid - 10\% (max 30 requests per second)
    \end{itemize}
    \item Extensions
    \begin{itemize}
        \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
        \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
        \item Do with Import Timeseries with error data which will go through extensions.
    \end{itemize}
    \item Export Timeseries
    \begin{itemize}
        \item Plan for 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
        \item Have mixture of data: Scalar - 70\%, Vector (Multi-Scalar) - 20\%, Grid - 10\% (Use the Imported - Data before and verify against Extensions)
    \end{itemize}
    \item Import + Extension + Export + Timeseries Queries (All)
    \begin{itemize}
        \item Plan for 30 minutes of test run with the request size of 1hr (60min) data.
        \item Plan for 30 minutes of test run with the request size of 30min data.
        \item Plan for 30 minutes of test run with the request size of 15min data.
        \item Plan for 30 minutes of test run with the request size of 15min data with Auto Scaling.
        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan run with enabling the Auto Scaling. (total 2 hours)
    \end{itemize}
\end{enumerate}

\subsection{Test Plan Observe Metrics}
\label{subse:test_plan_metrics}
During the performance analysis, following metrics are use to measure the performance of the system.
\begin{itemize}
    \item Throughput - Number of requests that can be process per unit time. Normally for \acrshort{wdias} performance observations, it uses \acrfull{rps} in order to measure the throughput.
    \item Latency - Time taken for response back to the sent request to the system. Normally it measures with milliseconds (ms) in the \acrshort{wdias}. During the performance analysis, it measures the minimum response time, maximum response time, the average response time, and standard deviation. The standard deviation measures the mean distance of the values to their average.It gives an idea of the dispersion or variability of the measures to their mean value. So, if the deviation value is low compared to the mean value, it will indicate that the measures are not dispersed (or mostly close to the mean value) and that the mean value is significant. Other than that, it measure the response time into 90\% percentile, while gives best response time up to 90\% percent of the responses.
    \item Resource Utilization - Resource Utilization is calculated based on the CPU and Memory usage via \acrshort{k8s} metrics server. It calculates the resource utilization over 60 seconds of time window. Network usage is getting based on the actual physical machines.
    \item Auto Scaling - The \acrshort{wdias} is running with two configurations. First is, since it is running the microservice as docker containers, it allow to increase or shrink the resource usage and share the resources within a physical machine. Second is, running with auto scaling enabled for the microservice which are using higher resources.
\end{itemize}

### 2020-02-08 results/sec_3-observations.tex
Update Obs Full test 24 and 48 request size

\section{Observations}

\subsection{Full work load test}

\subsubsection{Test with hourly (24) data}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 60min data}
\label{tab:obs_all_60_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_transaction_throughtput_vs_threads.png}
    \caption{Performance All Test 60 minutes - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_60m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_percentiles.png}
    \caption{Performance All Test 60 minutes - Response times Percentiles}
    \label{fi:test_obs_all_60m_latency_percentile}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
    \caption{Performance All Test 60 minutes - Latency against server hits}
    \label{fi:test_obs_all_60m_latency}
\end{figure}

\subsubsection{Test with 30min (48) data}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 30min data}
\label{tab:obs_all_30_min_summary}
\end{table}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_transaction_throughtput_vs_threads.png}
    \caption{Performance All Test 30 minutes - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_30m_throughtput}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_percentiles.png}
    \caption{Performance All Test 30 minutes - Response times Percentiles}
    \label{fi:test_obs_all_30m_latency_percentile}
\end{figure}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
    \caption{Performance All Test 30 minutes - Latency against server hits}
    \label{fi:test_obs_all_30m_latency}
\end{figure}

\subsubsection{Test with 15min (96) data}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 15min data}
\label{tab:obs_all_15_min_summary}
\end{table}

@@

\subsubsection{Load test with \acrfull{k8s} auto pod scaling}
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
    \caption{Performance All Test 15min Interval - Auto Scaling Resource Usage of Import and Export Modules }
    \label{fi:obs_all_auto_15m_import_export_res}
\end{figure}

@@

\subsection{Compare with other systems}

Throughput
Latency
Resource Utilization
Auto Scaling/Scalability

>>>>

\section{Observations}
According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:work_load}.

Following \ref{subse:obs_test_plan_all_60min}, \ref{subse:obs_test_plan_all_30min}, \ref{subse:obs_test_plan_all_15min} and \ref{subse:obs_test_plan_all_auto_15min} sections discussed about the observations collected with performing the Full test plan (also known as All test plan) over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size. Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.

\subsection{Full Test with hourly data (24 Request Size)}
\label{subse:obs_test_plan_all_60min}
After running the All test plan with 60 minutes (24 data points), it observed the data summary of \ref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 60min data}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the request are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries are similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the request perform within same amount of time, hence the standard deviation is smaller. Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms. Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \ref{se:test_plan}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
    \caption{Performance All Test 60 minutes - Response Time vs Threads}
    \label{fi:test_obs_all_60m_response_vs_threads}
\end{figure}
\ref{fi:test_obs_all_60m_response_vs_threads} show the response time against the number of active threads. As the graph show, the response time kept same while increasing the number of active threads against each test case. This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
When number of active threads increased more than 122, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
    \caption{Performance All Test 60 minutes - Latency against server hits}
    \label{fi:test_obs_all_60m_latency}
\end{figure}
\ref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
The conclusion of giving static latency while increasing the number of requests in \ref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \ref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.

\subsection{Full Test with 30min data (48 Request Size)}
\label{subse:obs_test_plan_all_30min}
This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII Grid files per each insert request. It performed 310k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 30min data}
\label{tab:obs_all_30_min_summary}
\end{table}
\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \ref{subse:obs_test_plan_all_60min}. And the results are almost similar to the observations in \ref{tab:obs_all_60_min_summary}. This implies that, even the request size is increased, the \acrshort{wdias} can perform better same as the with smaller size of data.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
    \caption{Performance All Test 30 minutes - Response Time vs Threads}
    \label{fi:test_obs_all_30m_response_vs_threads}
\end{figure}
\ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads. As the graph show, the response time kept same while increasing the number of active threads against each test case. This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
When number of active threads increased more than 110, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data. This graph is similar to the \ref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
    \caption{Performance All Test 30 minutes - Latency against server hits}
    \label{fi:test_obs_all_30m_latency}
\end{figure}
\ref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
This graph also conclude that, over the time latency does not change very much. But during the peak load, it shows some variation in insert and retrieve of Grid timeseries.
When compared to \ref{fi:test_obs_all_60m_latency}, the latencies for insert and retrieve Grid timeseries increase by some amount.

\subsection{Full Test with 15min data (96 Request Size)}
\label{subse:obs_test_plan_all_15min}
\begin{table}[]
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\caption{Throughput and Latency of All test cases with 15min data}
\label{tab:obs_all_15_min_summary}
\end{table}

@@

\subsection{Full Load test with \acrfull{k8s} auto pod scaling}
\label{subse:obs_test_plan_all_auto_15min}
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
    \caption{Performance All Test 15min Interval - Auto Scaling Resource Usage of Import and Export Modules }
    \label{fi:obs_all_auto_15m_import_export_res}
\end{figure}

@@
